HO unification from object language to meta language

### 2024-03-30 paper/main.tex
alternative syntax for examples
rename bound vars
indentation

Once a \linketa is activated, it can be removed from \linkStore,
otherwise, the link is kept for a further iteration of \elpiIn{progress}. Note
that this link progression enforce
\cref{prop:nf,inv:linklhs,inv:link-eta-right}: we never commit a term in
the \Ho substitution, since we make unification only when we know that the 
terms are no more \maybeeta, and when \lhs is no more a variable or \rhs is 
no more a \maybeeta, the link is removed from \linkStore.

\printAll
  {{\elpiIn{flam x\ fapp [fuva X, x] ~\Uo~fcon"f"}}}
  {{A \Ue f}}
  {{\mapping{X}{X'}{1}}}
  {{\linketaM{}{A}{\lambda x.X'_{x}}}}

@@

In \cref{sec:basic-comp-limitations}, we have given two unification problems to
be run one after the other. In the following table we present the entry problem,
its compiled version, with the corresponding list of mapping and links.
%
\printAll
  {{\elpiIn{flam x\ flam y\ fapp [fuva X, y, x] == flam x\ flam y\ x},
    \elpiIn{flam x\ fapp [fcon"f", fapp [fuva X, x], x] == fuva Y}}}
  {{E0 == \lambda x.\lambda y.x,
    E3 == E5}}
  {{\mapping{Y}{E5}{0},
    \mapping{X}{E2}{2}}}
  {{\linketaM{c0}{E4_{c0}}{\lambda x.E2_{c0 x}},
    \linketaM{}{E3}{\lambda x.(f~E4_{x}~x)},
    \linketaM{}{E0}{\lambda x.E1_{x}},
    \linketaM{c0}{E1_{c0}}{\lambda x.E2_{x c0}}}}

We see that the \elpiIn{maybe-eta} as detected $\lambda xy.F \appsep y \appsep
x$ and $\lambda x.f\appsep (F \appsep x) \appsep x$ and replaced them with
respectively the \Ho vars $X$ and $Z$. $X$ is linked with $\lambda x.Y_x$, $Y$
has arity $1$ and is $\eta$-linked with $\lambda y.H\appsep y \appsep x$ and $Z$
is linked to the term $\lambda x.f \appsep G_{x}~x$. However, the mapping
returned by the compilation, does not breaks \cref{inv:map-bijective}: the \Fo{}
variable $F$ is mapped to two different \Ho variables. To address this problem
and enforce \cref{inv:map-bijective}, we clean the mapping with a second phase
after the compilation. This phase is called \elpiIn{map-deduplication}.

>>>>

Once a \linketa is activated, it can be removed from \linkStore,
otherwise, the link is kept for a further iteration of \elpiIn{progress}. Note
that this link progression enforce
\cref{prop:nf,inv:linklhs,inv:link-eta-right}: we never commit a term in
the \Ho substitution, since we make unification only when we know that the 
terms are no more \maybeeta, and when \lhs is no more a variable or \rhs is 
no more a \maybeeta, the link is removed from \linkStore.
% \printAll
%   {{\elpiIn{flam x\ fapp [fuva X, x] ~\Uo~fcon"f"}}}
%   {{A \Ue f}}
%   {{\mapping{X}{X'}{1}}}
%   {{\linketaM{}{A}{\lambda x.X'_{x}}}}
$$
\begin{array}{l}
  \mathcal{P} = \{~ \lambda x.X \appsep x \Uo f ~\}\\
  \mathcal{T} = \{~ A \Ue f ~\}\\
  \mathbb{M} = \{~ \mapping{X}{B}{1} ~\}\\
  \linkStore \;= \{~ \linketaM{}{A}{\lambda x.B_{x ~\}}}
\end{array}
$$

@@

In \cref{sec:basic-comp-limitations}, we have given two unification problems to
be run one after the other. In the following table we present the entry problem,
its compiled version, with the corresponding list of mapping and links.

\printAll
  {{\elpiIn{flam x\ flam y\ fapp [fuva X, y, x] == flam x\ flam y\ x},
    \elpiIn{flam x\ fapp [fcon"f", fapp [fuva X, x], x] == fuva Y}}}
  {{E0 == \lambda x.\lambda y.x,
    E3 == E5}}
  {{\mapping{Y}{E5}{0},
    \mapping{X}{E2}{2}}}
  {{\linketaM{c0}{E4_{c0}}{\lambda x.E2_{c0 x}},
    \linketaM{}{E3}{\lambda x.(f~E4_{x}~x)},
    \linketaM{}{E0}{\lambda x.E1_{x}},
    \linketaM{c0}{E1_{c0}}{\lambda x.E2_{x c0}}}}
$$
{\arraycolsep=2pt \begin{array}{rrclrcl}
    \mathcal{P} = \{ &
       \lambda x.\lambda y.X \appsep y \appsep x & \Uo & \lambda x.\lambda y. x & \quad
       \lambda x. f \appsep (X \appsep x) \appsep x & \Uo&  Y ~\}\\
    \mathcal{T} = \{ &
       A &\Ue& \lambda x.\lambda y.x & \quad
       D &\Ue& F ~\}\\
    \mathbb{M} = \{ & \multicolumn{6}{l}{
      \mapping{Y}{F}{0} \quad
      \mapping{X}{C}{2} ~\}}\\
    \linkStore \;= \Big\{  &
      \multicolumn{6}{l}{ \begin{array}{ll}
          \linketaM{}{A}{\lambda x.B_{x}} & \quad
          \linketaM{x}{B_{x}}{\lambda y.C_{y x}}\\
          \linketaM{}{D}{\lambda x.(f~E_{x}~x)} & \quad
          \linketaM{y}{E_{y}}{\lambda w.C_{y w}}
      \end{array} ~\Big\}}
\end{array}}
$$
\marginpar{aggiustare i nomi delle variabili nel testo}
We see that the \elpiIn{maybe-eta} as detected $\lambda xy.F \appsep y \appsep
x$ and $\lambda x.f\appsep (F \appsep x) \appsep x$ and replaced them with
respectively the \Ho vars $X$ and $Z$. $X$ is linked with $\lambda x.Y_x$, $Y$
has arity $1$ and is $\eta$-linked with $\lambda y.H\appsep y \appsep x$ and $Z$
is linked to the term $\lambda x.f \appsep G_{x}~x$. However, the mapping
returned by the compilation, does not breaks \cref{inv:map-bijective}: the \Fo{}
variable $F$ is mapped to two different \Ho variables. To address this problem
and enforce \cref{inv:map-bijective}, we clean the mapping with a second phase
after the compilation. This phase is called \elpiIn{map-deduplication}.
